% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font
%\usepackage{textcomp}
%\usepackage[showframe=true]{geometry}
\usepackage{enumitem}


\begin{document}

\name{He Li}
% \address used twice to have two lines of address
\address{San Francisco Bay Area}
\address{650-665-0436. lhlich@gmail.com}

\begin{resume}

\section{Professional Summary}
Senior Machine Learning Engineer with 6+ years at Meta and Uber, specializing in search quality, RAG systems, and LLM-based ranking. Proven track record of independently leading end-to-end ML projects from ideation to production with measurable business impact. PhD in Electrical and Computer Engineering with deep expertise in privacy-preserving systems and applied cryptography.

\section{Work \\ Experience} 

\textbf{Senior Machine Learning Engineer --- Applied AI\ \textbar\ Uber Technologies\ \textbar\ Dec 2024 -- Present}
\begin{itemize}\itemsep -2pt
    \item Led development of AI-generated profiles for Uber Eats restaurants and groceries, designing system workflow, data operations, and evaluation strategy; achieved global coverage with a cross-functional team.
    \item Designed and deployed user and store embeddings derived from AI-generated profiles as ranking signals; independently led end-to-end A/B testing and achieved statistically significant gains in CTR and feed-attributed CVR/order volume.
\end{itemize}

\textbf{Research Scientist\ \textbar\ Meta, Inc.\ \textbar\ Oct 2018 -- Nov 2024}\\
%Senior Research Scientist.
Senior Engineer in search AI and personalization
\begin{itemize}\itemsep -2pt
    \item Designed and implemented a Retrieval-Augmented Generation (RAG) workflow and product prototype, defining core use-cases and building an LLM evaluator to showcase potential, leading to organizational prioritization.
    \item Built a RAG library powering Meta AI chatbot experience, contributing to the initial launch.

    \item Independently originated and led the development of a recommendation system, overseeing the entire lifecycle from ideation to deployment, resulting in significant increases in business performance.
        \begin{itemize}\itemsep -2pt
        \item Designed the end-to-end architecture of the recommendation system and developed it. This includes data collection, feature extraction, deployment, and monitoring/alerting.
        \item Designed and kicked off multi-round multi-arm online experiments to evaluate model improvements and validate statistical significance.
        \item Proposed different quantitative approaches to improve ranking models, integrate them and launched ranking model with business metrics win. 
    \end{itemize}
    
    
    \item Led the development of LLM-based NLP signals for search query intent detection:
    \begin{itemize}\itemsep -2pt
        \item Developed core LLM through prompting, fine-tuning, and distillation.
        \item Integrated models into product pipeline and developed comprehensive evaluation frameworks.
        \item Collaborated cross-functionally with human annotators to improve model performance.
        \item Achieved significant offline relevance rating improvements.
    \end{itemize}
\end{itemize}

Tech lead in Machine learning infrastructure for fraud detection and enforcement
\begin{itemize}\itemsep -2pt
    \item Directed a team in migrating feature authoring and serving platforms, improving the scalability and monitoring of ML models used in fraud detection.
    \item Integrated cutting-edge ML architectures, including deep neural networks, transfer learning (with GNN/sequential embedding), and auto-ML frameworks to accelerate deployment and improve model performance.
    \item Promoted a culture of machine learning excellence through model fairness research and developed tools for recurring analysis.
\end{itemize}

Tech lead in billing experience personalization
\begin{itemize}\itemsep -2pt
    \item Led product and ML innovations on billing limits with a cross-functional team of 4+ engineers. Ensured upfront alignment, proposed core engineering designs, scoped timelines, and drove execution.
    \item Crafted and scoped projects for the billing experience personalization roadmap for 3+ engineers. Reviewed related eng and ML designs.
    \item Collaborated with cross-functional teams to roll out critical billing features, finalizing milestones and overseeing the process.
\end{itemize}

Machine Learning Engineer in fraud detection and enforcement
\begin{itemize}\itemsep -2pt
  \item Designed, developed, and deployed ML models for fraud detection and user trust assessment, reducing financial losses and user blockage.
  \item Proposed and implemented payment risk integration strategies for Instagram, developing fraud detection models that protected billions in annual revenue.
  \item Led incident investigations for fraud attacks with \$20Mn+ losses, quickly deploying ML models to prevent further damage, resolving the root cause in two weeks.
  \item Enhanced team capabilities in fraud detection by reviewing and retraining models, and exploring advanced embeddings.
\end{itemize}

\textbf{Software Engineer Intern\ \textbar\ Facebook, Inc.\ \textbar\ May 2016 -- Aug 2016}
\begin{itemize}[noitemsep]
\item Onboarded new product on secure service, which thwarts potential account takeover attacks. Worked on multiple codebase involving various programming languages under few guidance, and completed project individually.
\end{itemize}


\section{Research Experience}
\textbf{Research Assistant\ \textbar\ Virginia Tech\ \textbar\ Aug 2014 -- Oct 2018}
\begin{itemize}[noitemsep]
    \item Research domain: Privacy, applied cryptography, and lightweight authentication.
    \item Published academic works on privacy-preserving signature protocols, privacy-preserving resource allocation protocols, and lightweight authentication protocols.
\end{itemize}

\textbf{Research Assistant\ \textbar\ Shanghai Jiao Tong University, China\ \textbar\ May 2010 -- Apr 2013}
\begin{itemize}[noitemsep]
    \item Research domain: Cognitive radio and dynamic spectrum access.
    \item Published academic works on energy-efficient signal detection, user activity modeling, and decision optimization in cognitive radio.
\end{itemize}
    
\section{Skills}
\begin{itemize}\itemsep -2pt
    \item Programming Languages: Python, C/C++, Haskell, PHP, Bash
    \item Machine Learning Frameworks: PyTorch, PyTorch Lightning, Ray, Keras
    \item Big Data Processing: Spark, Hive, Presto/Trino
    \item Tools: Git, Mercurial
    \item Domains: Search Quality, Retrieval-Augmented Generation (RAG), Recommendation Systems, Natural Language Processing, LLM Fine-Tuning \& Distillation, Deep Learning, Distributed Systems, Fraud Detection
    \item Systems: Unix
\end{itemize}

\section{Education}
\textbf{Virginia Tech} PhD in Electrical and Computer Engineering, MS in Math\\
\textbf{Shanghai Jiao Tong University} MS and BS in electrical engineering

           
\section{Selected Publications}
\begin{itemize}[leftmargin=*]  \itemsep -2pt % reduce space between items

	\item \textbf{He Li}, Yaling Yang, Yanzhi Dou, Jung-Min (Jerry) Park and Kui Ren. "PeDSS: Privacy Enhanced and Database-Driven Dynamic spectrum Sharing". In  Int'l Conference on Computer Communications (INFOCOM) 2019.


	\item \textbf{He Li}, Yanzhi Dou, Chang Lu, Doug Zabransky, Yaling Yang, and Jung-Min Park. Preserving incumbent users' location privacy in the 3.5 ghz band. In Dynamic Spectrum Access Networks (DYSPAN), 2018 IEEE International Symposium on. IEEE, 2018.
	
	\item \textbf{He Li}, Yaling Yang, Yanzhi Dou, Chang Lu, Doug Zabransky, and Jung-Min(Jerry) Park. "Comparison of incumbent user privacy preserving technologies in database driven dynamic spectrum access systems". 13th EAI International Conference on Cognitive Radio Oriented Wireless Networ (CrownCom 2018).

	\item Vireshwar Kumar, \textbf{He Li}, Jung-Min(Jerry) Park, and Kaigui Bian. "Enforcement in spectrum sharing: Crowd-sourced blind authentication of co-channel transmitters" [C]. 2018 IEEE Intl Symposium on Dynamic Spectrum Access Networks (DySPAN), Seoul, South Korea, Oct. 2018

	\item Douglas Zabransky, \textbf{He Li}, Chang Lu, and Yaling Yang. "SZ-SAS: A Framework for Preserving Incumbent User Privacy in SAS-based DSA Systems". 13th EAI International Conference on Cognitive Radio Oriented Wireless Networ (CrownCom 2018).

				\item Yanzhi Dou, Kexiong Zeng, \textbf{He Li}, Yaling Yang, Bo Gao, Kui Ren, Shaoqian Li. ``$ P^{2} $-SAS: Privacy-Preserving Centralized Dynamic Spectrum Access System"[J]. IEEE Journal on Selected Areas in Communications, 2017, 35(1): 173-187
					

                 \item Vireshwar Kumar, \textbf{He Li}, Jung-Min (Jerry) Park, Kaigui Bian, Yaling Yang, ``Group Signatures with Probabilistic Revocation: A Computationally-Scalable Approach for Providing Privacy-Preserving Authentication",  In Proceedings of the 22nd ACM SIGSAC Conference on Computer and Communications Security (CCS '15). ACM, New York, NY, USA, 1334-1345. (128 out of 646)
                \item Yanzhi Dou, Kexiong Curtis Zeng, \textbf{He Li}, Yaling Yang, Bo Gao, Chaowen Guan, Kui Ren, and Shaoqian Li. ``$P^2$-SAS: Preserving Users' Privacy in Centralized Dynamic Spectrum Access Systems." Proceedings of the 17th ACM MobiHoc (2016).


                \end{itemize}                  
 

% \section{AWARDS}
%                  \begin{itemize}[leftmargin=*]  \itemsep -2pt % reduce space between items
%                     \item Second Prize in the 8th National Post-graduate Mathmatical Contest in Modeling, 2011
%                     \item Excellent Academic Scholarship (first class), 2011
%                     \item First class Blackberry Scholarship , 2011
%                     \item Third Prize in National Undergraduate Electronic Design Contest, Shanghai division, 2009
%                     \item Excellent Academic Scholarship for three years (40 of 900 selected), 2006-2009
%                 \end{itemize}



     
\end{resume}
\end{document}